\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/experiments.tex

\srm{note somewhere that imputation requires both training and running model, and state why this is reasonable / the only choice}

>>>>

For every imputation inserted into the query plan, a new statistical model is instantiated and trained before being used for imputation.
Although it is tempting to further optimize query execution in \ProjectName{} by pre-training imputation models while the analyst begins to make queries,
this is not desirable because the specific rows of data, set of complete attributes, and set of attributes to impute are not known until runtime.
Furthermore, at that point, it may make more sense to specify a coherent model over the entire base table instead.
